A unified pseudo-$C_\ell$ framework

### 2018-08-31 doc/Paper/main.tex
merged, added CCL ref

\lstset{ %
language=python,                % choose the language of the code
basicstyle=\footnotesize\ttfamily,       % the size of the fonts that are used for the code
numbers=left,                   % where to put the line-numbers
numberstyle=\footnotesize,      % the size of the fonts that are used for the line-numbers
stepnumber=1,                   % the step between two line-numbers. If it is 1 each line will be numbered
numbersep=5pt,                  % how far the line-numbers are from the code
backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
showspaces=false,               % show spaces adding particular underscores
showstringspaces=false,         % underline spaces within strings
showtabs=false,                 % show tabs within strings adding particular underscores
frame=false,           % adds a frame around the code
tabsize=2,          % sets default tabsize to 2 spaces
captionpos=b,           % sets the caption-position to bottom
breaklines=true,        % sets automatic line breaking
breakatwhitespace=false,    % sets if automatic breaks should only happen at whitespace
escapeinside={\%*}{*)}          % if you want to add a comment within your code
}
%\usepackage[colorlinks,linkcolor=red,citecolor=blue,urlcolor=blue ]{hyperref}
 %\hypersetup{draft}
\newcommand{\nv}{\hat{\boldsymbol{\theta}}}
\newcommand{\wtj}[6]{\left(\begin{array}{ccc} #1 & #2 & #3\\#4 & #5 & #6\end{array} \right)}
\newcommand{\nmt}{{\tt NaMaster}}
\newcommand{\va}{{\mathbf{a}}}
\newcommand{\vb}{{\mathbf{b}}}
\newcommand{\mM}{{\sf M}}
\newcommand{\mI}{{\mathds{1}}}

@@

          \item {\bf Signal:} we generate maps of the galaxy overdensity $\delta$ and of the shear field $(\gamma_1,\gamma_2)$ for a redshift bin centred at $z\simeq1$ with a width $\Delta z\sim0.1$ and Gaussian photo-$z$ tails with width $\sigma_z=0.06$. For $\delta_g$ we assume unit bias $b(z)=1$ and no contributions from redshift-space distortions or magnification. For $\gamma$, we assume no contribution from intrinsic alignments. The maps are generated as Gaussian realizations of the corresponding angular power spectra computed with the Core Cosmology Library \todo{cite if paper is out} for cosmological parameters compatible with the 2015 Planck measurements~\citet{2016A&A...594A..13P}. These power spectra are shown in Fig. \ref{fig:lss_cls}. Sample realizations of $\delta$ and $\gamma$ can be seen in Figures \ref{fig:lss_mocks_sph} and \ref{fig:lss_mocks_flat} for the curved-sky and flat-sky cases respectively.

>>>>

\lstset{ %
language=python,                % choose the language of the code
basicstyle=\footnotesize\ttfamily,       % the size of the fonts that are used for the code
numbers=left,                   % where to put the line-numbers
numberstyle=\footnotesize,      % the size of the fonts that are used for the line-numbers
stepnumber=1,                   % the step between two line-numbers. If it is 1 each line will be numbered
numbersep=5pt,                  % how far the line-numbers are from the code
backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
showspaces=false,               % show spaces adding particular underscores
showstringspaces=false,         % underline spaces within strings
showtabs=false,                 % show tabs within strings adding particular underscores
frame=false,           % adds a frame around the code
tabsize=2,          % sets default tabsize to 2 spaces
captionpos=b,           % sets the caption-position to bottom
breaklines=true,        % sets automatic line breaking
breakatwhitespace=false,    % sets if automatic breaks should only happen at whitespace
escapeinside={\%*}{*)}          % if you want to add a comment within your code
}
\newcommand{\nv}{\hat{\boldsymbol{\theta}}}
\newcommand{\wtj}[6]{\left(\begin{array}{ccc} #1 & #2 & #3\\#4 & #5 & #6\end{array} \right)}
\newcommand{\nmt}{{\tt NaMaster}}
\newcommand{\va}{{\mathbf{a}}}
\newcommand{\vb}{{\mathbf{b}}}
\newcommand{\mM}{{\sf M}}
\newcommand{\mI}{{\mathds{1}}}

@@

          \item {\bf Signal:} we generate maps of the galaxy overdensity $\delta$ and of the shear field $(\gamma_1,\gamma_2)$ for a redshift bin centred at $z\simeq1$ with a width $\Delta z\sim0.1$ and Gaussian photo-$z$ tails with width $\sigma_z=0.06$. For $\delta_g$ we assume unit bias $b(z)=1$ and no contributions from redshift-space distortions or magnification. For $\gamma$, we assume no contribution from intrinsic alignments. The maps are generated as Gaussian realizations of the corresponding angular power spectra computed with the Core Cosmology Library\footnote{\url{https://github.com/LSSTDESC/CCL/pulls}} for cosmological parameters compatible with the 2015 Planck measurements~\citet{2016A&A...594A..13P}. These power spectra are shown in Fig. \ref{fig:lss_cls}. Sample realizations of $\delta$ and $\gamma$ can be seen in Figures \ref{fig:lss_mocks_sph} and \ref{fig:lss_mocks_flat} for the curved-sky and flat-sky cases respectively.
